---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rbirds.pkg

<!-- badges: start -->
<!-- badges: end -->

The goal of rbirds.pkg is to allow users to explore the bird_counts data using various functions. The data for this package is about various bird species counted by birdwatchers in Hamilton area of Ontario. Birdwatchers have counted birds they saw or heard in a day. Birds are counted every year around Christmas time, since 1921.

The package contains various functions which help to answer questions like:

- which are the most counted birds? 
- the most counted bird in each year? 
- top five most counted birds in each year?
- how many hours it took to count total birds in a year?. 

The package also contains a function which runs a shiny application created to analyse various aspects of the data.

## Installation

You can install the development version of rbirds.pkg from [rbirds.pkg](https://etc5523-2022.github.io/rpkg-Adarsh098/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2022/rpkg-Adarsh098")
```

## Example

This function is used to load the rbirds.pkg package.

```{r example}
library(rbirds.pkg)
```

This function allows the user to view the top five most counted birds in the data set.
```{r ex1}
most_birds()
```

This function helps to determine how many hours it took to count approximate number of birds.

```{r ex2}
count_by_hours(8000)
```



